Forecasting the 2024 U.S. Presidential Election

### 2024-11-04 paper/paper.qmd
Survey Updated

---
title: "Forecasting the 2024 U.S. Presidential Election"
author: 
  - Jason Yang
  - Another author
thanks: "Code and data are available at: [https://github.com/Jerryx2020/US_election_prediction/tree/main]."
date: "`r format(Sys.Date() - 1, '%A, %B %d, %Y')`" #chatgpt assisted how to create a custom date for due date November 4
date-format: long
abstract: ""
format: pdf
number-sections: true
bibliography: references.bib
---

@@

- Polling Percentage (PCT): Represents the percentage of respondents in a poll who support a specific candidate
- Numeric Grade (numeric_grade): Represents the rating of the pollster to indicate their quality
- Sample Size (sample_size): size of the respondents participating in the poll
- State (state): the state of the poll was taken in 
- End_date: the day the poll ended
- Start_date: the day the poll started

@@

\begin{align*}
\text{pct}_i &= \beta_0 + \beta_1 \cdot \text{numeric\_grade}_i + \beta_2 \cdot \text{sample\_size}_i + \sum_{k=1}^{K} \delta_k \cdot \text{state}_{ik} + \beta_4 \cdot \text{end\_date}_i + \epsilon_i,
\end{align*}

- pct: The percentage of the vote or support that the candidate received in the poll (e.g., 51.0 for Kamala Harris, 48.0 for Donald Trump).
- numeric_grade: A numeric rating given to the pollster to indicate their quality or reliability (e.g., 3.0).
- sample_size: The total number of respondents participating in the poll (e.g., 2712).
- state: The U.S. state where the poll was conducted or focused, if applicable.
- end_date: The date the poll ended (e.g., 10/11/24).
- $\epsilon_i$: The error term for poll accounting for variability not explained by the predictors.

@@

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

@@

Our target population is voters aged 18 and above, with a sample size of approximately 10,000 responses, 200 responses from each state, to ensure a statistically significance at the national level and within key demographic groups. To achieve balanced representation, we will employ stratified random sampling based on age, gender, race/ethnicity, education, region, and urban/rural status. This approach will involve weighting responses using recent census data and voter turnout statistics to address any demographic discrepancies.

For recruitment, we will combine online survey panels, social media outreach, and targeted telephone recruitment. These methods are chosen to increase accessibility for harder-to-reach demographics, such as older adults and rural residents. To encourage participation, we will offer modest incentives, such as a small monetary compensation or entry into a prize draw. All data collection will be conducted through a reliable survey platform—Google Forms.

The survey itself will be concise and straightforward, focusing on voting intentions, key issues, and demographic information. For data validation, in the survey, we will include attention-check questions as respondents are very likely to complete the form for an entry into a prize draw. We will also conduct multiple waves of the survey, we will adopt a "poll-of-polls" approach, aggregating responses from different waves while applying weights based on relevance.

@@

Ethically, our approach prioritizes respondent privacy and data security. We will ensure that participants’ responses remain anonymous and that all data is handled securely. Transparency is also essential; respondents will be informed about the survey’s sponsorship, methodology, and data use

@@

## Idealized Survey

@@

## Survey Copy 
Welcome to our survey! We are conducting research to understand public perceptions and opinions related to the upcoming 2024 Presidential Election. Your responses are valuable in helping us gain insight into voter perspectives and preferences.

Contact Information: For any questions regarding this survey, please contact:

Name: [Jason Yang]
Email: ["jzc.yang@mail.utoronto.ca"]
Phone: ["123-234-5678"]

Your responses are confidential and will be used only for research purposes. This survey will take approximately [estimated time] to complete.

1. **Who do you intend to vote for in the 2024 U.S. Presidential Election?**
  - Kamala Harris (Democratic Party)
  - Donald Trump (Republican Party)
  - Undecided 
  - Other:

2. **How certain are you about your choice?  **
  - Very Certain
  - Somewhat certain
  - Unsure

3. **Which of the following issues are most important in deciding your vote? (Select up to 3)**
  - Economy and jobs
  - Healthcare
  - Climate Change
  - Education
  - Immigration
  - National Security 
  - Social justice and Equality 
  - Abortion rights
  - Gun control
  - Other:

4. **What is your age?**
  - 18-24
  - 24-34
  - 35-44
  - 45-54
  - 55-64
  - 65 or older

5. **What is your gender?**
  - Male 
  - Female
  - Non-binary/Other
  - Prefer not to say

6. **What is your race/ethnicity? (Select all that apply)**
  - White
  - Black or African American 
  - Hispanic or Latino 
  - Asian
  - Native American or Alaska Native
  - Native Hawaiian or Other Pacific Islander 
  - Other:

7. **In which U.S. state do you currently reside?**
  - ___

8. **If you voted in 2020, who did you vote for?**
  - Joe Biden 
  - Donald Trump 
  - Other:

Thank you for taking the time to complete our survey. Your input is greatly appreciated and will contribute to our understanding of public opinion for the upcoming 2024 Presidential Election.

>>>>

---
title: "Forecasting the 2024 U.S. Presidential Election"
author: 
  - Jason Yang
  - Jerry Xia 
  - Peter Fan
thanks: "Code and data are available at: [https://github.com/Jerryx2020/US_election_prediction/tree/main]."
date: "`r format(Sys.Date() - 1, '%A, %B %d, %Y')`" #chatgpt assisted how to create a custom date for due date November 4
date-format: long
abstract: ""
format: pdf
header-includes: 
  - \usepackage{pdfpages}
number-sections: true
bibliography: references.bib
---

@@

- Polling Percentage (PCT): Represents the percentage of respondents in a poll who support a specific candidate
- Pollster: Represents the name of the polling organization that conducted the poll. 
- Candidate: The name of the candidate in the poll
- Sample Size (sample_size): size of the respondents participating in the poll
- State (state): the state of the poll was taken in 
- End_date: the day the poll ended
- Start_date: the day the poll started

@@

\begin{align*}
\text{pct}_i &= \beta_0 + \beta_1 \cdot \text{pollster}_i + \beta_2 \cdot \text{sample\_size}_i + \sum_{k=1}^{K} \delta_k \cdot \text{state}_{ik} + \beta_4 \cdot \text{end\_date}_i + \beta_5 \cdot \text{candidate}_i + \epsilon_i,
\end{align*}

Where

- $\beta_0$ is the expected value of PCT when all predictor variables are zero, intercept 
- $\beta_1$ captures the effect pollsters have on the response variable 
- $\beta_2$ captures the effect sample_size have on the response variable
- $\delta_k$ captures the difference in PCT between states
- $\beta_4$ captures the expected change in PCT for each additional unit increase in the end date variable 
- $\beta_5$ captures the difference in PCT associated with difference candidates

@@

@@

Our target population is voters aged 18 and above, with a sample size of approximately 10,000 responses, 200 responses from each state, to ensure  statistical significance at the national level and within key demographic groups. To achieve balanced representation, we will employ stratified random sampling based on age, gender, race/ethnicity, education, region, and urban/rural status. This approach will involve weighting responses using recent census data and voter turnout statistics to address any demographic discrepancies.

We will combine online survey panels, social media outreach, and targeted telephone recruitment. These methods are chosen to increase accessibility for harder-to-reach demographics, such as older adults and rural residents. To encourage participation, we will offer modest incentives, such as a small monetary compensation or entry into a prize draw. All data collection will be conducted through a reliable survey platform—Google Forms.

The survey itself will be concise and straightforward, focusing on voting intentions, key issues, and demographic information. For data validation, the survey will include attention-check questions as respondents are very likely to complete the form for an entry into a prize draw. We will also conduct multiple waves of the survey, we will adopt a "poll-of-polls" approach, aggregating responses from different waves while applying weights based on relevance.

@@

To ensure data validity, IP addresses would be recorded to prevent multiple submissions from the same source. Additionally, cookies would be implemented to prevent users from retaking the survey on the same device. Finally, we will verify respondents' email addresses to ensure uniqueness.

Ethically, our approach prioritizes respondent privacy and data security. We will ensure that participants’ responses remain anonymous and that all data is handled securely. Transparency is also essential; respondents will be informed about the survey’s sponsorship, methodology, and data use.

@@

## Budget Allocation

- Sampling and Data Collection (Advertisements and Recruitment Platforms): $40,000
- Participant Incentives (Prize Pool): $20,000
- Survey Design and Testing: $20,000
- Data Analysis and Validation: $20,000

# Idealized Survey

@@

## Survey Copy

\includepdf[pages=-]{../other/Survey/Survey.pdf}
